% Created 2024-08-27 Tue 10:14
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\setcounter{secnumdepth}{2}
\author{Fabrice Niessen}
\date{\today}
\title{Example of Tasks}
\hypersetup{
 pdfauthor={Fabrice Niessen},
 pdftitle={Example of Tasks},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 29.4 (Org mode 9.6.28)}, 
 pdflang={English}}
\begin{document}

\maketitle
\setcounter{tocdepth}{4}
\tableofcontents

\noindent\rule{\textwidth}{0.5pt}

\section{Work\hfill{}\textsc{work}}
\label{sec:orgf142beb}
Only work tasks in this list.

\subsection{Marketing}
\label{sec:org9a4f501}
Project "Corporate Marketing".

\subsubsection*{Background and research}
\label{sec:org1e34b4e}

\paragraph*{{\bfseries\sffamily TODO} Who are the competitors?\hfill{}\textsc{FLAGGED}}
\label{sec:orga7533e8}

\begin{itemize}
\item {\bfseries\sffamily TODO} What are our product's advantages?
\label{sec:org4169327}

\item {\bfseries\sffamily TODO} Target market
\label{sec:orge14c9e4}
\end{itemize}

\paragraph*{{\bfseries\sffamily TODO} Elevator pitch}
\label{sec:orgcddad80}

\subsubsection*{PR firm}
\label{sec:org9d85deb}

\paragraph*{{\bfseries\sffamily TODO} Call Laura about PR firm\hfill{}\textsc{phone}}
\label{sec:orgf32111e}

\paragraph*{STRT Interview PR firm candidates}
\label{sec:org5ab1a91}

\subsubsection*{Advertising campaign}
\label{sec:org75c2848}

\paragraph*{{\bfseries\sffamily TODO} Call Joe}
\label{sec:org2caa59c}

\subsubsection*{Plan conference}
\label{sec:org5d61045}

Calendar events/invitations.

\paragraph*{{\bfseries\sffamily TODO} Recruit volunteers}
\label{sec:org1095c15}

\paragraph*{{\bfseries\sffamily TODO} Make sure responses are coming back}
\label{sec:org2e98d51}

\subsection{Operations}
\label{sec:orgfac50de}

\subsubsection*{{\bfseries\sffamily TODO} Update database to latest version}
\label{sec:orgde363d5}

\subsubsection*{{\bfseries\sffamily TODO} Update Website}
\label{sec:org2000c58}

Update blog.

\subsection{Travel}
\label{sec:orgc616fc6}

\subsubsection*{Boston}
\label{sec:org4510e59}

\paragraph*{{\bfseries\sffamily TODO} Find a flight}
\label{sec:orge833028}

\paragraph*{{\bfseries\sffamily TODO} Book hotel room}
\label{sec:orge084ab6}

\paragraph*{{\bfseries\sffamily TODO} Schedule meetings}
\label{sec:orgd4bc3ce}

\paragraph*{{\bfseries\sffamily TODO} Submit expense report}
\label{sec:orga16bd98}

\noindent\rule{\textwidth}{0.5pt}

\section{Personal\hfill{}\textsc{personal}}
\label{sec:org38f1b21}
\subsection{Reading}
\label{sec:orgc4323b3}

\subsubsection*{{\bfseries\sffamily DONE} Read "Getting Things Done"}
\label{sec:orgb454ed7}

\subsection{Health}
\label{sec:org1e473e2}

\subsubsection*{{\bfseries\sffamily TODO} Make dentist appointment\hfill{}\textsc{phone}}
\label{sec:org2432f02}

\subsubsection*{{\bfseries\sffamily TODO} Go to the gym}
\label{sec:org6533bf6}
It should be as natural to some as showering or eating.

\subsubsection*{{\bfseries\sffamily TODO} Do jogging}
\label{sec:orgc404b6b}

Marathon = 42,195 km.

\subsection{Finance}
\label{sec:org7076def}

\subsubsection*{{\bfseries\sffamily TODO} Pay electricity bill\hfill{}\textsc{FLAGGED}}
\label{sec:org87a9be4}

\subsubsection*{{\bfseries\sffamily TODO} Renew newspaper subscription}
\label{sec:orgd91f9af}

\subsubsection*{{\bfseries\sffamily TODO} Cancel insurance\hfill{}\textsc{mail}}
\label{sec:orgeb18016}

\subsection{Chores}
\label{sec:org2c27144}

\subsubsection*{{\bfseries\sffamily TODO} Buy milk}
\label{sec:orgc50ef27}

\subsubsection*{{\bfseries\sffamily TODO} Buy dog food}
\label{sec:org082c865}

\subsubsection*{WAIT Mail package to Susan}
\label{sec:org9fd48ad}

\subsubsection*{{\bfseries\sffamily TODO} Buy groceries}
\label{sec:org5d52484}

\subsubsection*{{\bfseries\sffamily TODO} Mow the lawn}
\label{sec:org2fc09cb}

\subsubsection*{{\bfseries\sffamily TODO} Get a haircut}
\label{sec:org7e0c6bc}

\subsubsection*{{\bfseries\sffamily TODO} Buy anniversary present}
\label{sec:org11fa685}

\subsubsection*{{\bfseries\sffamily TODO} Take out trash}
\label{sec:orgf7fcb12}

\subsubsection*{{\bfseries\sffamily TODO} Get the car fixed}
\label{sec:org847189e}

\subsection{Recreation}
\label{sec:org6f959f0}

\subsubsection*{{\bfseries\sffamily TODO} Go to concert}
\label{sec:orgf69b94a}
\end{document}
